Twisted eleven-dimensional supergravity

### 2021-10-21 matrix.tex

\subsection{(Non)formality and homotopy transfer} 
\label{s:ht}

We produce the following homotopy data:
\begin{equation}
\begin{tikzcd}
\arrow[loop left]{l}{K}(\Pi \cE , \delta^{(1)})\arrow[r, shift left, "q"] &(E(5,10) \oplus \CC_b \, , \, 0)\arrow[l, shift left, "i"] \: ,
\end{tikzcd}
\end{equation}

@@

\parsec[s:altglobal]

In \S \ref{s:altdfn} we gave an equivalent description of the 11-dimensional theory as a deformation of the BF action $S_{BF,0}$ by the functional $\til J$.

\subsection{Twisted matrix model}

>>>>

\subsection{(Non)formality and homotopy transfer} 
\label{s:ht}
We proceed to the proof of part (2) of Theorem \ref{thm:global}. 
To do this, we first produce the following homotopy data:
\begin{equation}
\begin{tikzcd}
\arrow[loop left]{l}{K}(\Pi \cE , \delta^{(1)})\arrow[r, shift left, "q"] &(E(5,10) \oplus \CC_b \, , \, 0)\arrow[l, shift left, "i"] \: ,
\end{tikzcd}
\end{equation}

@@

%\parsec[s:altglobal]

%In \S \ref{s:altdfn} we gave an equivalent description of the 11-dimensional theory as a deformation of the BF action $S_{BF,0}$ by the functional $\til J$.

%\subsection{Twisted matrix model}

### 2021-10-21 nonmin.tex

We replace this linear BRST complex, up to quasi-isomorphism, with a smaller BRST complex. 
Consider the complex
\beqn
\Omega^{0,\bu}_Z \hotimes \Omega^{\bu,\bu}_X \hotimes \Omega^\bu_L = \oplus_{k =0}^3 \Omega^{0,\bu}_Z \hotimes \Omega^{k,\bu}_X \hotimes \Omega^\bu_L 
%[-k] 
\eeqn
which is equipped with the differential $\dbar^z + \dbar^w + \del^w + \d_{\RR}$. 
Write $\alpha = \alpha^0 + \cdots + \alpha^3$ for a field in this complex, using the decomposition on the right hand side.

@@

>>>>

We replace this linear BRST complex, up to quasi-isomorphism, with a smaller BRST complex. 
Consider the complex
\beqn
\Omega^{0,\bu}_Z \hotimes \Omega^{\bu,\bu}_W \hotimes \Omega^\bu_L = \oplus_{k =0}^3 \Omega^{0,\bu}_Z \hotimes \Omega^{k,\bu}_W \hotimes \Omega^\bu_L 
%[-k] 
\eeqn
which is equipped with the differential $\dbar^z + \dbar^w + \del^w + \d_{\RR}$. 
Write $\alpha = \alpha^0 + \cdots + \alpha^3$ for a field in this complex, using the decomposition on the right hand side.

@@

We first substitute the values for the fields in \eqref{eqn:g2map} into the original 11-dimensional action. 
The terms which are at least cubic in the action in \eqref{eqn:delta1} become
\beqn
\int \frac{1}{1-\til\alpha^3} \left(\frac12 \del^w \alpha^1 (\til \alpha^2)^2 \d^2 z + \alpha^2 \del^z \alpha^1 \del^z \alpha^0 + \alpha^3 \del^z \alpha^0 \del^z \alpha^0 \right) .
\eeqn
Here, $\til \alpha^2$ denotes the element of $\Omega^{0,\bu}_Z \hotimes \PV^{1,\bu}_W \hotimes \Omega^\bu_L$ corresponding to $\alpha^2$ determined by the Calabi--Yau form $\d^3 w$. 
There is only one cubic term left in \eqref{eqn:delta2} when we substitute the fields according to \eqref{eqn:g2map}.
It is
\beqn
\frac16 \int \alpha^1 \del^z \alpha^1 \del^z \alpha^1. 
\eeqn

Notice that the total action is of the form 
\beqn\label{eqn:pcs1}
S_{pCS} (\alpha) + \int \frac{1}{1-\til\alpha^3} \left(\frac12 \del^w \alpha^1 (\til \alpha^2)^2 \d^2 z + \til\alpha^3 \alpha^2 \del^z \alpha^1 \del^z \alpha^0 + \til\alpha^3 \alpha^3 \del^z \alpha^0 \del^z \alpha^0 \right)
\eeqn
where $S_{pCS}$ is the Poisson Chern--Simons action in \eqref{eqn:pcsaction}.

We will show that the terms not appearing in $S_{pCS}(\alpha)$ are cohomologically trivial. 
First, consider the odd local functional
\beqn\label{eqn:triv1}
\int \frac{1}{1 - \til \alpha^3} \alpha^2 (\til \alpha^2)^2 .
\eeqn
Applying the linearized BRST operator (in the non-minimal twist) this becomes 
\[
\int \frac{1}{1 - \til \alpha^3} \del^w \alpha^1 (\til \alpha^2)^2 +  \int \frac{1}{1 - \til \alpha^3} \del^w (\alpha^2) \alpha^2 (\til \alpha^2)^2 .
\]
The first term in this expression agrees the first term in parentheses in \eqref{eqn:pcs1}.
The second term is zero for symmetry reasons. 
Thus, \eqref{eqn:triv1} trivializes the first term in parentheses in \eqref{eqn:pcs1}.

It remains to trivialize the remaining terms in parentheses. 
To do this, we fix a primitive $\eta$ of the holomorphic volume form $\d^3 w$. 
That is, $\eta$ is a holomorphic two-form on $W$ satisfying $\del \eta = \d^3 w$. 
Consider the (non-translation invariant) odd local functional
\[
\int \frac{1}{1-\til \alpha^3} \eta (\til \alpha^3)^2 \del^z \alpha^1 \del^z \alpha^0   .
\]
Using $\del^w \eta = \d^3 w$, we see that this functional trivializes the remaining terms in parentheses in \eqref{eqn:pcs1}.
This completes the argument.
